Reionization Planck 2018 ...

### 2020-06-23 results/notes.tex

\section{Outline (in progress)}

\begin{enumerate}
	\item{Intro}
	\item{Background}
		\begin{itemize}
			\item{Reionization Principal Components}	
			\item{Kernel Density Estimate}
		\end{itemize}
	\item{Planck 2018 PC results:\\
		- can discuss discrepancy here on high-redshift tau($>$15) constraints. }
	\item{Effective Likelihood}
		\begin{itemize}
			\item{Code Description}
			\item{Examples - one and two parameter models}
		\end{itemize}
	\item{Discussion}

\end{enumerate}

@@

\begin{figure}[t]
\includegraphics[width=0.40\textwidth]{plots/plot_tau_gtz.pdf}
\caption{...
}
\label{fig:}
\end{figure}

\begin{figure}
\includegraphics[width=0.40\textwidth]{plots/pl18_pc_zmax30_pliklite_srollv2_1015_tau_posterior_fraccov_1p0_burnin_10000_yes_norm_gaussian0p1_0p12_0p14.pdf}
\caption{...
}
\label{fig:}
\end{figure}

>>>>

@@

Trying to collect all of our tests here.\\

List of tests:\\
-

\begin{figure}[t]
\includegraphics[width=0.40\textwidth]{../paper/plots/plot_tau_gtz.pdf}
\caption{...
}
\label{fig:}
\end{figure}

\begin{figure}
\includegraphics[width=0.40\textwidth]{python_kde_test/pl18_pc_zmax30_pliklite_srollv2_1015_tau_posterior_fraccov_1p0_burnin_10000_yes_norm_gaussian0p1_0p12_0p14.pdf}
\caption{...
}
\label{fig:}
\end{figure}
